\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Discussion: Limits

Let us highlight some innovations in the contributions presented in this paper. First, the generic heterosynaptic model is formalized from first principles for optimal detection of the event-based spatiotemporal motifs, whereas [] uses a correlation-based heuristic, which we have proven to be less efficient. Moreover, in comparison to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly inform on the logit (inverse sigmoid of the probability) of detecting each spatio-temporal spiking pattern. Another novelty is that the model simultaneously learns the weights and the delays, while for example the polychronization model~\citep{Izhikevich 2006} only learns the weights using STDP while the delays are randomly drawn and their values frozen. Moreover, the model is evaluated on a realistic task, while models such as tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. The main contribution is to provide a model that is suitable for any type of spatio-temporal spiking patterns and that can be trained in a supervised way by providing a dataset of supervision pairs. This allows for a more flexible definition of the model using this properly labeled dataset instead of relying on a careful description of the physical rules governing a task, e.g., the luminance conservation principle for motion detection~~citep{benosman_asynchronous_2012, dardelet}.

@@

We ientified several limits to our model,
the major of which we will now detail. First,
the full framework is based on discrete time which
is incompatible with the analogous nature of biological
time. We have used the binning of time to ease
the implementation of the computational framework
on conventional hardware, especially GPUs,
and in particular by using the three-dimensional
convolution. We have tested the effect of this time
bin size and have shown it does not impact
the results shown here. This is consistent with the
relative robustness of other ff event-based
frameworks such as thots, where accuracy was
not changed when jittering input spikes by
up to 1ms noise (grimaldi zz]. This hints
at including analytically a precision term in
the temporal value of incoming spikes, a
mechanism potentially implemented by the
n 5 ms smoothing at the level of the PSC
of conventional synapses. Furthermore, it is
possible to overcome the problem using a purely
even d- based scheme. Indeed, it is not necessary to
compute voltage males between two spikes (Morrison)
and to define a purely event-driven framework.
A further limit is that the model that
we defined is purely feed-forward. It
results that the spikes generated by post-synaptic
neurons are produced solely based on the
information in the classical receptive field.
However, it is known that neurons in a
layer may interact using lateral interaction
[charane Lorry and that this may be the
basis of computational principles, for instance
of binding neighboring orientations (Bednar).
Moreover, neural information is modulated by
feedback information, for instance do distinguish
figure from background (Roefsema J and
has proven to be essential in building realistic
models of the primary visual areas (Boutin 2020
Boutin rozo feedback , Boutin '2oz]. It is nd
currently possible to implant these recurrent
connections (lateral or feedback), mainly because
of our use of convolutions. However the generic
model is capable of including this by
inserting spikes in the list of spikes reaching
the pipe-synaptic addresses. While possible
in theory, it should be properly adapted
in practice such that these recurrent
connections do not reach outside an
homeostatic state ( a death or a
blow-up of activity).
Suchreccarrentatvityweential
to implement predictive or anticipative
processes . This is essential in a neural
system as it contains multiple different
delays which necessitates a temporal
alignment (Hoogendoorn 2019]. This was
previously modeled to explain for instance
the flash - lag visual illusion (Khoei 2017)
As was previously started " ... " (reminet
20174], and our hetero-synaptic model
would provide with a simple and elegant
solution to that problem.

>>>>

Let us highlight some innovations in the contributions presented in this paper. First, the generic heterosynaptic model is formalized from first principles for optimal detection of the event-based spatiotemporal motifs, whereas [] uses a correlation-based heuristic, which we have proven to be less efficient. Moreover, in comparison to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly inform on the logit (inverse sigmoid of the probability) of detecting each spatio-temporal spiking pattern. Another novelty is that the model simultaneously learns the weights and the delays, while for example the polychronization model~\citep{Izhikevich 2006} only learns the weights using STDP while the delays are randomly drawn and their values frozen. Moreover, the model is evaluated on a realistic task, while models such as tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. The main contribution is to provide a model that is suitable for any type of spatio-temporal spiking patterns and that can be trained in a supervised way by providing a dataset of supervision pairs. This allows for a more flexible definition of the model using this properly labeled dataset instead of relying on a careful description of the physical rules governing a task, e.g., the luminance conservation principle for motion detection~\citep{benosman_asynchronous_2012, dardelet}.

@@

We identified several limits to our model, the major of which we will now detail. First, the full framework is based on discrete binning of time which is incompatible with the analogous nature of biological time. We have used this binning to ease the implementation of the computational framework on conventional hardware, especially GPUs, and in particular to be able to use three-dimensional convolutions. We have tested the effect of the time bin size and have shown it does not impact the results presented in this paper. This is consistent with the relative robustness of other  event-based frameworks such as HOTS (Lagorce 2017), where accuracy was not changed when jittering input spikes by up to 1ms of noise (grimaldi 2022). This hints at including analytically a precision term in the temporal value of incoming spikes, a mechanism potentially implemented by the approx 5 ms smoothing which is implemented at the level of the PSC of synapses. Furthermore, it is possible to overcome the problem using a purely even-driven based scheme. Indeed, it is not necessary to compute voltage males between two spikes (Morrison) and to define a purely event-driven framework. Such an architecture should provide with promising speed-ups for the computations.

A further limit is that the model that we defined is purely feed-forward. As a consequence, the spikes generated by post-synaptic neurons are produced solely based on the information in the classical receptive field. However, it is known that neurons in a layer may interact using lateral interaction (chavane 2022) and that this may be the basis of computational principles, for instance of binding of neighboring orientations which may be a basis for image categorization (Bednar). Moreover, neural information is modulated by feedback information, for instance do distinguish figure from background (Roelfsema 2016) and has proven to be essential in building realistic models of the primary visual areas (Boutin 2020 Boutin 2020 feedback , Boutin 2022). It is not currently possible to implement these recurrent connections in our implementation (lateral or feedback), mainly because of our use of convolutions. However the generic theoretical model is capable of including these by inserting spikes in the list of spikes reaching the pre-synaptic addresses. While possible in theory, it should be properly adapted in practice such that these recurrent connections do not amplify neural activity outside an homeostatic state (by a death or a blow-up of activity).

Such recurrent activity would be essential to implement predictive or anticipative processes . This is essential in a neural system as it contains multiple different delays which necessitates a temporal alignment (Hoogendoorn 2019]. This was previously modeled to explain for instance the flash - lag visual illusion (Khoei 2017) As was previously started " ... " (Perrinet 2014], and our hetero-synaptic model would provide with a simple and elegant solution to that problem.
